---
title: "fsPDA: An R Package"
author: "Zhentao Shi and Yishu Wang"
date: \today
output:
  rmarkdown::pdf_document: default
  '# rmarkdown::html_vignette': default
vignette: >
  %\VignetteIndexEntry{Forward-Selected Panel Data Approach}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
description: nothing
geometry: margin=1in
bibliography: REFERENCES.bib
biblio-style: apalike
link-citations: yes
fontsize: 11pt
urlcolor: blue
header-includes:
- \usepackage{graphics}
- \usepackage{pgfplots}
- \usepackage{caption}
- \usepackage{setspace}
- \singlespacing
---  

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction


Program evaluation is an important economemtric topic. 
@hsiao2012panel's *panel data approach* (PDA) is one of the leading methods for program evaluation.
To extend PDA to big data environments, 
@shi2019forward ([arXiv: 1908.05894](https://arxiv.org/abs/1908.05894)) propose the *forward-selected panel data approach* (fsPDA)
which uses the forward selection algorithm to select a small number
of control units, and then employ these selected units to estimates and conduct inference for the average treatment effect (ATE).


Forward selection is a well-known greedy variable selection method 
[@hastie2009bible]. After forward selection, fsPDA suggest 
using the selected control units to run OLS, predicting the counterfactual,
and calculating the standard *t*-statistic for hypothesis testing.


@shi2019forward bring forth the procedure and establish its asymptotic guarantee. 
This document introduces the R package `fsPDA` ([https://github.com/zhentaoshi/fsPDA](https://github.com/zhentaoshi/fsPDA))
which automates the procedure.


## Usage
To install the R package, run
```{r, eval=FALSE}
devtools::install_github("zhentaoshi/fsPDA/R_pkg_fsPDA")
```

The package is documented with complete help files for all functions and datasets. 
The work horse function is `est.fsPDA`:
```{r, eval=FALSE}
est.fsPDA <- function(treated, control, treatment_start, date = NULL, lrvar_lag = NULL) 
```
The arguments of the function are

*  `treated`: A $T$-dimensional time series vector of the treated unit.
*  `control`: A $T\times N$ panel matrix with each column being a control unit.
*  `treatment_start`: An integer specifying the period treatment starts. 
*  `date`:  A $T$-dimensional vector of date class or any meaningful numerical sequence. The  default setting `NULL` uses all time observations `1:length(treated)`.
* `lrvar_lag`: A non-negative integer for the maximum lag with the Bartlett kernel for the Newey-West long-run variance estimator. The default choice `NULL` specifies `floor((length(treated)-treatment_start+1)^(1/4))`.

This function returns an objected of the class `fsPDA` with following components:

* `select`: The number and the identities of selected units when the forward selection is terminated by the modified Bayesian information criterion.
* `in_sample`: In-sample fitting before the treatment data. 
* `out_of_sample`: Out-of-sample counterfactual prediction and the time-varying treate effect after the treatment data. 
* `ATE`: The estimated ATE, the corresponding long-run variance, *t*-statistic for the test of zero ATE, and the associated p-value.

To help visualize the raw data, fitted value and the counterfactual prediction, we also provide a `plot` method for the class `fsPDA`. See the help file of `plot.fsPDA` for its usage.


## Datasets

The package contains two datasets. `china_import` is the China's luxury watch import 
in the empirical application of Section 5 of @shi2019forward. 
`HCW` is original dataset from in @hsiao2012panel. 
These two datasets are employed to demonstrate the usage of the package.

## Demonstrations


First, we replicate the study of China's luxury watch import. 
The statistical inference outcomes are printed.

```{r}
library(fsPDA)
data("china_import")
date_import <- names(china_import$treated)

date_import <- names(china_import$treated)
result <- est.fsPDA(
  treated = china_import$treated, control = china_import$control,
  treatment_start = which(date_import == china_import$intervention_time),
  date = as.Date(paste(substr(date_import, 1, 4), "-", 
                       substr(date_import, 5, 6), "-01", sep = ""))
)

print(result$ATE)
```

A time series graph with a clear legend is provided by the generic `plot` method. 

```{r}
plot(result, tlab = "Year", ylab = "Monthly Growth Rate")
```

Next, we apply fsPDA to the `HCW` dataset of 24 countries and territories. 
```{r}
data("HCW")
result <- est.fsPDA(
  treated = HCW$panel[, 1], 
  control = HCW$panel[, -1],
  treatment_start = HCW$T1 + 1,
  date = as.Date(paste(substr(HCW$quarter, 1, 4), "-", 
            (as.numeric(substr(HCW$quarter, 6, 6)) - 1) * 3 + 1, "-1", sep = ""))
)

print(result$select$control)
```
The forward selection is automatically terminated by the modified BIC after selecting 7 economies. The discrepancy between the realized Hong Kong real GDP growth and the 
estimated counterfactual can is discernible.

```{r}
plot(result, tlab = "Year", ylab = "HK GDP Growth Rate")
```




## References
