---
title: "Forward-Selected Panel Data Approach"
author: "Zhentao Shi and Yishu Wang"
date: \today
output:
  rmarkdown::pdf_document: default
  '# rmarkdown::html_vignette': default
vignette: >
  %\VignetteIndexEntry{Forward-Selected Panel Data Approach}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
description: nothing
geometry: margin=1in
bibliography: REFERENCES.bib
biblio-style: apalike
link-citations: yes
fontsize: 12pt
urlcolor: blue
header-includes:
- \usepackage{graphics}
- \usepackage{pgfplots}
- \usepackage{caption}
- \usepackage{setspace}
- \singlespacing
---  
  
  
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fsPDA)
```



#### Description

Function implementing forward-selected panel data approach in @shi2019forward.

#### Installation

```{r, eval=FALSE}
devtools::install_github("zhentaoshi/fsPDA/R_pkg_fsPDA")
```

#### Usage

```{r, eval=FALSE}
library(fsPDA)
data("china_import")

treated = china_import$treated
control = china_import$control
intervention_time = china_import$intervention_time

result=est.fsPDA(treated, control,
            treatment_start = which(names(treated) == intervention_time),
            date = as.Date(paste(substr(names(treated),1,4), "-", substr(names(treated), 5, 6), "-01", sep="")))
```

#### Arguments

| Argument          |                                                              |
| :---------------- | ------------------------------------------------------------ |
| `treated`         | Numeric. A $T$-dimensional time series vector of treated units. |
| `control`         | Numeric. A $T\times N$ panel matrix with each column being a control unit. |
| `treatment_start` | An integer specifying the period treatment starts. Should set to lie between $T/2$ and $T$ to ensure enough pre-treatment observations. |
| `date`            | Date or numeric. A $T$-dimensional vector of date class or any meaningful numerical sequence. By default, if set to be `NULL`, `1:length(treated)` is used. |
| `lrvar_lag`       | A non-negative integer specifying the maximum lag with Bartlett kernel for the Newey-West long-run variance estimator. By default, if set to be `NULL`, `floor((length(treated)-treatment_start+1)^(1/4))` is used. Cannot set to be larger than `floor(sqrt(length(treated)-treatment_start+1))`. |
| `plot`            | Logical. Should a `ggplot` object be included in the return list and printed? If set to be `TRUE`, `ggplot2` package is needed as dependency. |

#### Value

| Return          |                                                              |
| --------------- | ------------------------------------------------------------ |
| `select`        | A list containing feature selection results, where `dim` is the number of selected units, `control` is the vector indicates the selected units, `coef` contains the coefficient estimates, and `RSquared` is the in-sample $R^2$. |
| `in_sample`     | A data frame with in-sample fitted values.                   |
| `out_of_sample` | A data frame with out-of-sample counterfactual predicts and treatment effect estimates. |
| `ATE`           | A numeric vector containing estimate of average treatment effect (ATE), its long-run variance, t-statistic, and p-value to test if ATE is statistically 0. |
| `plot`          | A `ggplot` object. Some post-plot arguments of `ggplot` can be added additionally, for example, `labs`. |


https://github.com/zhentaoshi/fsPDA

#### Examples

```{r, eval=FALSE}
library(fsPDA)
library(ggplot2)

data("china_import")

treated = china_import$treated
control = china_import$control
intervention_time = china_import$intervention_time

result=est.fsPDA(treated, control,
             treatment_start = which(names(treated) == intervention_time),
             date = as.Date(paste(substr(names(treated),1,4), "-", substr(names(treated), 5, 6), "-01", sep="")))

# print(result$plot+labs(x="Year",y="Monthly Growth Rate"))
```


## References
